---
title: "main-nitesh"
author: "Nitesh Singh Jaswal"
date: "March 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
inter.data = read.csv("International-graduate-student-survey-results.csv")
summary(inter.data)
# Q39
acad.experience = rowSums(select(inter.data, Q39_1 , Q39_2 , Q39_3 , Q39_4 , Q39_5 , Q39_6 , Q39_7), na.rm = FALSE, dims = 1)/7
acad.experience = round(acad.experience)
# Q43
acad.challenges =  as.numeric(inter.data$Q43_1 | inter.data$Q43_2 |inter.data$Q43_3 |inter.data$Q43_4 |inter.data$Q43_5 |inter.data$Q43_7)
inter.small = select(inter.data, Q2, Q3, Q4, Q5, Q22, Q40, Q41, Q42, Q28)
inter.small$Q39 = acad.experience
inter.small$Q43 = acad.challenges
```

Variables to consider (Know of the land):
Age: Q2
Gender: Q3
Degree pursuing: Q4
Discipline of degree: Q5
What is your home country: Q22

Response variable:
Want to remain in US after graduation: Q28 

Predictor Variables:
Academic experience in comparison with your home country: Q39
Treatment by Prof/Colleagues in comparison with your home country: Q40
Treatment by Prof/Colleagues if you went back to your home country: Q41
Adjustment to American educational culture: Q42
Challenges encountered in the US: Q43





