---
title: "main-nitesh"
author: "Nitesh Singh Jaswal"
date: "March 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(arm)
library(broom)
cb_palette = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r}
inter.data = read.csv("International-graduate-student-survey-results.csv")
# summary(inter.data)
# Q39
acad.experience = rowSums(dplyr::select(inter.data, Q39_1 , Q39_2 , Q39_3 , Q39_4 , Q39_5 , Q39_6 , Q39_7), na.rm = FALSE, dims = 1)/7
# acad.experience = factor(round(acad.experience))

# Q43
acad.challenges =  factor(as.numeric(inter.data$Q43_1 | inter.data$Q43_2 |inter.data$Q43_3 |inter.data$Q43_4 |inter.data$Q43_5 |inter.data$Q43_7))
inter.small = dplyr::select(inter.data, Q2, Q3, Q4, Q5, Q22, Q40, Q41, Q42, Q28)
inter.small$Q39 = acad.experience
inter.small$Q43 = acad.challenges

# Factoring gender
inter.small$Q3 = factor(inter.small$Q3, labels = c("Male", "Female", "Not Specified"))
# Factoring Studies
inter.small$Q5 = factor(inter.small$Q5)
levels(inter.small$Q5) <- c("Life sciences", "Physical sciences", "Engineering", "Mathematics", "Computer science", "Other")
# Factoring countries
inter.small$country <- as.factor(ifelse(inter.small$Q22==44, "China", ifelse(inter.small$Q22==91, "India", "Other")))
levels(inter.small$country) <- c("China", "India", "Other")

# Recoding and Factoring the response in order
inter.small$likelihood = recode(inter.small$Q28, `1` = 2, `3` = 1, `2` = 0)
inter.small$likelihood = as.factor(inter.small$likelihood)
levels(inter.small$likelihood) <- c("Unlikely", "Somewhat Likely", "Very Likely")
```
EDA
```{r}
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q3)) + stat_count() + facet_wrap(~as.factor(Q5))
```
```{r}
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q3)) + stat_count() + facet_wrap(~as.factor(country))
```

```{r}
# Stay in US by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = (Q39), ..count.., fill = likelihood)) + geom_density(position = "fill") + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = (Q39)^3, ..count.., fill = likelihood)) + geom_density(position = "fill") + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

```
Since Q39 has been converted to a numeric variable, should we apply some transformation over this to smooth out the distribution? We noticed that by cubing the data we were able to obtain some pattern in our data as opposed to not applying any transformation whatsoever.
```{r}
# Stay in US by Discipline
ggplot(inter.small, aes(x = (Q39), ..count.., fill = likelihood)) + geom_density(position = "fill") + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q5)

# Stay in US by Degree
ggplot(inter.small, aes(x = (Q39), fill = likelihood)) + geom_histogram(binwidth=1) + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)
# DIZZ IZZ GOOD

# Stay in US by country
ggplot(inter.small, aes(x = (Q39), ..count.., fill = likelihood)) + geom_density(position = "fill") + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~country)
```

```{r}
# Treatment by colleagues and professors by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q40, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors by Gender") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

# Treatment by colleagues and professors by Degree
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q40, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)

# Treatment by colleagues and professors by Discipline
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q40, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors by Discipline") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q5)

# Treatment by colleagues and professors by country
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q40, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors by country") + scale_fill_manual(values = cb_palette) + facet_wrap(~country)
```

```{r}
# Treatment by colleagues and professors in home country by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Gender") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

# Treatment by colleagues and professors by Degree
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)

# Treatment by colleagues and professors by Discipline
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Discipline") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q5)

# Treatment by colleagues and professors by country
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Country") + scale_fill_manual(values = cb_palette) + facet_wrap(~country)
```

```{r}
# Adjustment to american culture by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Gender") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

# Treatment by colleagues and professors by Degree
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)

# Treatment by colleagues and professors by Discipline
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Discipline") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q5)

# Treatment by colleagues and professors by country
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Country") + scale_fill_manual(values = cb_palette) + facet_wrap(~country)
```


```{r}
# Acad Challenges vs Response
ggplot(inter.small, aes(x = Q43, y = Q28)) + geom_jitter(width = 0.2, height = 0.2)
# Acad experience vs Response
ggplot(inter.small, aes(x = Q39, y = Q28)) + geom_jitter(width = 0.2, height = 0.2)
# Acad experience and Acad Challenges vs Response
ggplot(inter.small, aes(x = Q39, y = Q43, color = Q28)) + geom_jitter(width = 0.2, height = 0.2)
# Age vs Response
ggplot(inter.small, aes(x = Q2, y = Q28)) + geom_jitter(width = 0.2, height = 0.2)
# Discipline of degree vs response
ggplot(inter.small, aes(x = Q2, y = Q28)) + geom_jitter(width = 0.2, height = 0.2)


ggplot(inter.small, aes(x = Q39, fill = likelihood)) + stat_count()
ggplot(inter.small, aes(x = Q43, fill = Q28)) + stat_count()
# summary(inter.small$Q42)
```

```{r}
# Preliminary model
inter.polr = polr(likelihood~Q39*Q40*Q41*Q43, data = inter.small)
display(inter.polr)
# inter.polr.df = augment(inter.polr)
apply.fitted = fitted.values(inter.polr)[,2] + 2 * fitted.values(inter.polr)[,3]
apply.resid = inter.small$Q28 - apply.fitted
inter.polr.df = data.frame(inter.small, .fitted = apply.fitted, .resid = apply.resid)
# var(inter.polr.df$.fitted)/(var(inter.polr.df$.fitted) + var(inter.polr.df$.resid))
gg = ggplot(inter.polr.df, aes(x = Q43, y = .resid)) + geom_point()
gg + geom_smooth(method.args = list(degree = 1))
```

```{r}
ggplot(inter.small, aes(x = Q40)) + stat_count(color = "#E69F00", fill = "#E69F00") + labs(x="Response", y="Number of Students", title="Treatment by colleagues and professors in the US in comparison with those \n in your home country", caption="<1> = Treated much worse ... <5> = Treated much better") + theme_bw()
```

```{r}
ggplot(inter.small, aes(x = Q41)) + stat_count(color = "#E69F00", fill = "#E69F00") + labs(x="Response", y="Number of Students", title="Treatment by colleagues and professors in your home country if you returned", caption="<1> = Treated much worse ... <5> = Treated much better") + theme_bw()
```

```{r}
ggplot(inter.small, aes(x = Q42)) + stat_count(color = "#E69F00", fill = "#E69F00") + labs(x="Response", y="Number of Students", title=" How well have you adjusted to American educational culture", caption="<1> = Did not adjusted well ... <5> = Adjusted well") + theme_bw()
```

```{r}
ggplot(inter.small, aes(x = factor(Q43, labels = c( "No challenges", "Some challenges", "Many challenges")))) + stat_count(color = "#E69F00", fill = "#E69F00") + labs(x="", y="Number of Students", title="Challenges encountered while adjusting to America") + theme_bw()
```


Questions to ask professor Luen:
1. Can we take mean of multiple discrete variables representing more or less the same parameter and treat it as a continuous variabele? For example, can we aggregate the various parameters representing academic experience and treat that value as a continuous variable representing a sort of academic experience score?
2. Can we use R^2 for polr to explain the variance

Variables to consider (Know of the land):
Age: Q2
Gender: Q3
Degree pursuing: Q4
Discipline of degree: Q5
What is your home country: Q22

Response variable:
Want to remain in US after graduation: Q28 

Predictor Variables:
Academic experience in comparison with your home country: Q39
Treatment by Prof/Colleagues in comparison with your home country: Q40
Treatment by Prof/Colleagues if you went back to your home country: Q41
Adjustment to American educational culture: Q42
Challenges encountered in the US: Q43





