---
title: "Project Discussion"
author: "Nitesh Singh Jaswal"
date: "April 11, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cb_palette = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r echo=FALSE}
inter.data = read.csv("International-graduate-student-survey-results.csv")
# summary(inter.data)
# Q39
acad.experience = rowSums(dplyr::select(inter.data, Q39_1 , Q39_2 , Q39_3 , Q39_4 , Q39_5 , Q39_6 , Q39_7), na.rm = FALSE, dims = 1)/7
# acad.experience = factor(round(acad.experience))

# Q43
acad.challenges =  factor(as.numeric(inter.data$Q43_1 | inter.data$Q43_2 |inter.data$Q43_3 |inter.data$Q43_4 |inter.data$Q43_5 |inter.data$Q43_7))
inter.small = dplyr::select(inter.data, Q2, Q3, Q4, Q5, Q22, Q40, Q41, Q42, Q28)
inter.small$Q39 = acad.experience
inter.small$Q43 = acad.challenges

# Factoring gender
inter.small$Q3 = factor(inter.small$Q3, labels = c("Male", "Female", "Not Specified"))
# Factoring Studies
inter.small$Q5 = factor(inter.small$Q5)
levels(inter.small$Q5) <- c("Life sciences", "Physical sciences", "Engineering", "Mathematics", "Computer science", "Other")
# Factoring countries
inter.small$country <- as.factor(ifelse(inter.small$Q22==44, "China", ifelse(inter.small$Q22==91, "India", "Other")))
levels(inter.small$country) <- c("China", "India", "Other")

# Recoding and Factoring the response in order
inter.small$likelihood = recode(inter.small$Q28, `1` = 2, `3` = 1, `2` = 0)
inter.small$likelihood = as.factor(inter.small$likelihood)
levels(inter.small$likelihood) <- c("Unlikely", "Somewhat Likely", "Very Likely")
```

### Does it make sense to apply some transformation on an artficially created numeric variable to smoothen the trend and make the pattern more prominent? We noticed that by cubing the data we were able to obtain some pattern in our data as opposed to not applying any transformation whatsoever
```{r}
# Stay in US by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = (Q39), ..count.., fill = likelihood)) + geom_density(position = "fill") + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = (Q39)^3, ..count.., fill = likelihood)) + geom_density(position = "fill") + ggtitle("Likelihood of staying in the US after graduation") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

```

### This is an interesting plot we got wherein we can finally see some clear trend in the likelihood of staying
```{r}
# Stay in US by Degree
ggplot(inter.small, aes(x = (Q39), ..count.., fill = likelihood)) + geom_bar(binwidth = 1, position = "fill") + ggtitle("Likelihood of staying in the US after graduation by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)
```
```{r}
ggplot(inter.small, aes(x = Q39)) + geom_bar(binwidth = 1) + ggtitle("Likelihood of staying in the US after graduation by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~likelihood + Q4)
```

### Some other plots we generated but were not intersting in our opinion

```{r}
# Treatment by colleagues and professors in home country by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Gender") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)

# Treatment by colleagues and professors by Degree
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)

# Treatment by colleagues and professors by Discipline
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Discipline") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q5)

# Treatment by colleagues and professors by country
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q41, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Treatment by colleagues and professors in home country by Country") + scale_fill_manual(values = cb_palette) + facet_wrap(~country)
```

```{r}
# Adjustment to american culture by Gender
ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Gender") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q3)


ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Degree") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q4)


ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Discipline") + scale_fill_manual(values = cb_palette) + facet_wrap(~Q5)


ggplot(inter.small[inter.small$Q3 %in% c("Male", "Female"),], aes(x = Q42, ..count.., fill = likelihood)) + stat_count(position = "fill") + ggtitle("Adjustment to american culture by Gender by Country") + scale_fill_manual(values = cb_palette) + facet_wrap(~country)
```